The eclipse of ASASSN-21qj

### 2022-12-29 src/tex/ms.tex
[showyourwork] overleaf sync

The sampling of the photometry enables determination of the reddening as a function of time during the eclipse.
%
The reddening is calculated in 20 day bins and plotted in Figure ZZZZ, showing that the reddening angle is very consistent over the duration of the eclipse, but that there is a suggestion that the reddening angle changes gradually during the ingress and egress.

>>>>

The sampling of the photometry enables determination of the reddening as a function of time during the eclipse.
%
The reddening is calculated in 20 day bins and plotted in Figure~\ref{fig:reddenanglevstime}, showing that the reddening angle is very consistent over the duration of the eclipse, but that there is a suggestion that the reddening angle changes gradually during the ingress and egress.

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/alpha_vs_time_aavso_fit.pdf}
\caption{Plot of reddening angle versus time over the central part of the eclipse. The reddening angle is calculated in 20 day bins. A linear fit is shown over the duration of the eclipse.}
        \label{fig:reddenanglevstime}
    \end{centering}
\end{figure}
